%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-17pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeSubHeadingListStart}{%
  \begin{itemize}[leftmargin=0.0in,label={},topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt]
}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{%
  \begin{itemize}[topsep=2pt,itemsep=1pt,parsep=0pt,partopsep=0pt]
}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeOrgHeading}[1]{
  \vspace{15pt} \item \textbf{#1}\vspace{-10pt}
}

\newcommand{\resumeSubheading}[4]{ \vspace{-2pt}
    \item \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r} 
        \textbf{#1} & \textbf{\small #2} \\ \textit{\small#3} & \textit{\small #4} \\ 
    \end{tabular*}\vspace{-7pt} 
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape \textbf{Timothe Roma}} \\ \vspace{5pt}
    Montreal, Quebec\\ \vspace{5pt}
    \small \raisebox{-0.1\height}\faPhone\ 613-240-4480 ~ \href{mailto:timothe.roma@mail.mcgill.ca}{\raisebox{-0.2\height}\faEnvelope\  \underline{timothe.roma@mail.mcgill.ca}} ~ 
    \href{https://linkedin.com/in/tim-roma/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/tim-roma/}}  ~
    \href{https://github.com/Timber868}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/Timber868}}
    \vspace{-8pt}
\end{center}
\vspace{6pt}



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\vspace{10pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Golang, Java, Python, C++, JavaScript/TypeScript} \\
     \textbf{Frameworks \& Web}{: Spring Boot, React.js, Vue.js} \\
     \textbf{Cloud \& DevOps}{: Kubernetes (Helm), Docker, GitLab CI/CD} \\
     \textbf{Databases}{: PostgreSQL, MySQL} \\
     \textbf{Developer Workflow}{: GitHub, AI-Assisted Development (Cursor, Copilot)}
    }}
 \end{itemize}
 \vspace{-20pt}


%-----------EXPERIENCE-----------
\section{Work Experience} 


\resumeSubHeadingListStart  

\resumeOrgHeading{Thales -- Full-Stack Software Engineer Co-op}
  % ==== DPOD (most recent) ====
\resumeProjectHeading
    {Data Protection on Demand Team $|$ \emph{Java, Spring Boot, Kubernetes, GitLab CI}}
    {05/2025 -- 09/2025}
  \resumeItemListStart
    \resumeItem{Replaced a deprecated dependency across 14 Spring Boot services, unblocking the migration from Java 11 to Java 17 by implementing a compatibility helper to preserve legacy behavior.}
    \resumeItem{Triggered GitLab CI pipelines to build and test service updates, deploying versioned artifacts via Helm to an isolated Kubernetes namespace for integration validation prior to promotion.}
    \resumeItem{Executed end-to-end tests across 14 services, diagnosing and resolving integration issues in IntelliJ prior to release.}
    \resumeItem{Increased unit test coverage and resolved SonarQube findings to reduce regression risk during the migration.}
  \resumeItemListEnd

% ==== LCH (earlier) ====
\resumeProjectHeading
    {Luna Cloud HSM Team $|$ \emph{Golang, Bash, Git, GitLab CI, Python}}
    {04/2024 -- 08/2024}
  \resumeItemListStart
    \resumeItem{Redesigned a Golang-based support tool to automate endpoint and security configuration diagnostics, programmatically reproducing client-reported errors.}
    \resumeItem{Produced structured terminal output and exportable reports that reduced manual troubleshooting effort; delivered 7 enhancements originally scoped for 2.}
    \resumeItem{Developed Bash automation to configure proxies, manage environment variables, build and execute Go services, and clean test artifacts for consistent endpoint testing.}
    \resumeItem{Presented the redesigned support tool to 55+ engineers, project owners, and stakeholders, demonstrating diagnostic improvements and operational impact.}
  \resumeItemListEnd

\vspace{3pt}

%-----------EXPERIENCE-----------
\section{Projects} 

% --- MCGILL ENGINEERING GAMES (Strong) ---
\resumeOrgHeading{McGill Engineering Games}

\resumeProjectHeading
    {VP Machine $|$ \emph{C++, Arduino, Embedded Systems, Motor Control}}
    {01/2025 -- 01/2026}
\resumeItemListStart
  \resumeItem{Led a 10+ person team that delivered a competition robot which achieved 50\% of total available points under strict build constraints; received the Partners’ Choice Award for resilience and innovation.}
  \resumeItem{Developed and tested C++/Arduino control firmware for two competition robots, tuning motor parameters and integrating Bluetooth communication.}
\resumeItemListEnd

\resumeProjectHeading
  {Software Team Member $|$ \emph{C++, Golang, CTF, Bash, Python, Java}}
  {07/2023 -- 01/2026}
\resumeItemListStart
  \resumeItem{Core member of a 7-person software team that won the Software Engineering competition three consecutive years (2024--2026), competing against 12 universities in time-constrained hackathon-style challenges.}
\resumeItemListEnd

% --- consulting rewrite ---
%If for consulting
\resumeProjectHeading
    {VP Machine $|$ \emph{Robotics Systems, C++/Arduino, Rapid Prototyping, Jira, Testing}}
    {01/2025 -- 01/2026}
\resumeItemListStart
    \resumeItem{Led a \textbf{10+ person} team and managed delivery through \textbf{50+ Jira tickets}, coordinating materials, meetings, testing, and rapid iteration under tight budget constraints.}
    \resumeItem{Translated a competition problem statement into a robotics strategy by analyzing constraints and terrain risks, identifying scoring optimizations, and iterating toward reliable solutions.}
    \resumeItem{Drove a key design pivot after a ramp increased mass beyond tolerance, leveraging terrain interaction to eliminate the ramp and restore lifting reliability under tight constraints.}
    \resumeItem{Presented solution rationale and performance trade-offs to a panel of professional engineer judges; earned the \textbf{Partners' Choice Award} for innovation and execution.}
\resumeItemListEnd

\resumeProjectHeading
  {Software Team Member $|$ \emph{C++/Go/Python, Rapid Problem-Solving, Technical Leadership}}
  {09/2023 -- 01/2026}
\resumeItemListStart
  \resumeItem{Core member of a \textbf{7-person} team that won the Software Engineering competition \textbf{three consecutive years (2024--2026)}, competing against 12 universities in time-constrained hackathon-style challenges.}
  \resumeItem{Owned \textbf{technical execution} during the 2026 competition by triaging problems, assigning work to \textbf{3 developers}, and coordinating submissions across multiple challenge categories.}
\resumeItemListEnd

% --- CS GAMES ---
\resumeOrgHeading{McGill Computer Science Games}

\resumeProjectHeading
  {Team Captain}
  {01/2025 -- 05/2026}
\resumeItemListStart
  \resumeItem{Led the 11-member McGill delegation at CS Games 2025, coordinating logistics and scheduling to ensure each member competed in at least two events; co-leading the 2026 delegation.}
  \resumeItem{Secured team funding through university grant applications and competed in CTF, DevOps, and Web Development events; edited and produced McGill’s official introduction video.}
\resumeItemListEnd

% for consulting 
\resumeProjectHeading
  {Team Captain}
  {01/2025 -- 05/2026}
\resumeItemListStart
  \resumeItem{Led an \textbf{11-member} McGill delegation at CS Games 2025, coordinating logistics and scheduling to ensure each member competed in \textbf{2+ events}; co-leading the 2026 delegation.}
  \resumeItem{Secured \textbf{\$2,000} in funding through university grant applications to cover most team expenses; managed external deliverables (official introduction video) and competed in CTF, DevOps, and Web Development events.}
\resumeItemListEnd

% --- RoomieRanks ---
\resumeProjectHeading
  {\textbf{RoomieRanks Website} $|$ \emph{Golang, MySQL, Vue.js}}
  {01/2025 -- 03/2025}
\resumeItemListStart
    \resumeItem{Implemented Vue.js pages end-to-end, integrating API calls and UI logic to deliver complete user flows.}
    \resumeItem{Built Golang backend services using interfaces and composition (Go-style OOP) for core features.}
    \resumeItem{Designed and evolved the MySQL data model (tables, relationships, constraints) for user/application data.}
    \resumeItem{Validated data correctness with targeted SQL sanity checks during debugging and feature iteration.}
\resumeItemListEnd

% --- McGill Formula Electric (LOW) ---
\resumeProjectHeading
  {\textbf{McGill Formula Electric Website} $|$ \emph{React.js, CSS, HTML, GitHub}}
  {10/2022 -- 07/2023}
\resumeItemListStart
  \resumeItem{Spearheaded three major components, including building the full 'Contact Us' page, enhancing user engagement and streamlining communication.}
  \resumeItem{Collaborated through GitHub and Asana to drive React-based development and coordination.}
  \resumeItem{Developed reusable components with modern patterns to streamline the development process.}
  \resumeItem{Balanced responsibilities in a hybrid setting, effectively managing both remote and in-person work.}
\resumeItemListEnd

% --- LockIn AI ---
\resumeProjectHeading
  {\textbf{LockIn AI (Hackathon Project)} $|$ \emph{Python, MediaPipe, React, ElevenLabs API}}
  {01/2026 -- 02/2026}
\resumeItemListStart
    \resumeItem{Integrated ElevenLabs text-to-speech by writing Python logic to call the API and generate refocus audio prompts.}
    \resumeItem{Contributed to the computer-vision pipeline using MediaPipe face detection and gaze/head-pose cues to classify whether a user is focused, enabling real-time UI feedback.}
    \resumeItem{Worked on the Python backend to capture and preprocess video frames and stream focus-state updates to a React dashboard via WebSocket; supported the character-based alert system.}
\resumeItemListEnd

% --- Decision Tree Learning (ECSE 250 A3) (LOW) ---
\resumeProjectHeading
  {\textbf{Decision Tree Classifier (ECSE 250)} $|$ \emph{Java, Decision Trees}}
  {11/2023 -- 12/2023}
\resumeItemListStart
    \resumeItem{Implemented a binary decision tree with threshold splits to classify traffic-light color (red/green) from 2D position.}
    \resumeItem{Trained the tree by recursively choosing split thresholds via information gain (entropy) and stopping at leaf criteria.}
    \resumeItem{Implemented inference via tree traversal to a leaf and evaluated performance using test misclassification rate.}
\resumeItemListEnd

% --- Computer Vision Coursework (ECSE 415) (LOW) ---
\resumeProjectHeading
  {\textbf{Computer Vision Assignments (ECSE 415)} $|$ \emph{Python, OpenCV, NumPy}}
  {01/2026 -- 02/2026}
\resumeItemListStart
    \resumeItem{Implemented core image operations and denoising filters (Gaussian/median), using NumPy/OpenCV.}
    \resumeItem{Built a Harris corner detection pipeline (gradients, smoothing, response, non-max suppression).}
    \resumeItem{Extracted and matched SIFT features and analyzed scale/rotation effects on matching quality.}
\resumeItemListEnd

% --- ECSE 321 Game Store ---
\resumeProjectHeading
  {\textbf{Game Store Platform} $|$ \emph{Vue.js, Java Spring Boot, PostgreSQL}}
  {09/2024 - 12/2024}
\resumeItemListStart
    \resumeItem{Developed the GameView page in Vue.js from the ground up: built dynamic price and promotion displays based on active offers:contentReference[oaicite:0]{index=0}, enabled customers to like or remove likes on reviews and let owners reply to reviews through conditionally rendered buttons:contentReference[oaicite:1]{index=1}, and added a reply form component for writing and submitting responses:contentReference[oaicite:2]{index=2}.}
    \resumeItem{Integrated API calls with Vue components to fetch game details and reviews, determine whether a user has liked a review:contentReference[oaicite:3]{index=3}, submit new reviews and replies:contentReference[oaicite:4]{index=4}, and handle add‑to‑cart/wishlist actions; implemented client‑side functions for liking/unliking reviews that update the UI and invoke backend endpoints:contentReference[oaicite:5]{index=5}.}
    \resumeItem{Extended the Spring Boot backend to support the new review features: added REST endpoints for checking if a user liked a review and for liking/unliking reviews in \texttt{ReviewController.java}:contentReference[oaicite:6]{index=6}, introduced a \texttt{hasReply} property to the review response DTO so the frontend can show reply buttons appropriately:contentReference[oaicite:7]{index=7}, and added service methods \texttt{checkHasLiked}, \texttt{addLike} and \texttt{removeLike} that use the new repository to manage likes:contentReference[oaicite:8]{index=8}:contentReference[oaicite:9]{index=9}.}
    \resumeItem{Redesigned the data model for review likes: created a \texttt{ReviewLike} entity that links each review to the customer who liked it:contentReference[oaicite:10]{index=10}, replaced the previous list of liked customers with a \texttt{reviewLikes} collection in the \texttt{Review} entity and computed the number of likes from it:contentReference[oaicite:11]{index=11}:contentReference[oaicite:12]{index=12}, added repository queries to detect if a user has liked a review:contentReference[oaicite:13]{index=13}, and wrote integration tests to verify the new endpoints, including checking that the \texttt{/likes} API correctly reports and updates like status:contentReference[oaicite:14]{index=14}.}
\resumeItemListEnd









\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\vspace{15pt}

\resumeSubHeadingListStart
\resumeSubheading   {McGill University}
    {Aug. 2022 - May. 2027}
    {Bachelor of Engineering, Software Engineering (Co-op) -- One Year Entrance Scholarship} 
    {Montreal, Quebec}
    
\resumeSubHeadingListEnd

\end{document}